Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-01 paper/paper.tex
some progress

TODO: mrf definition

@@

For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ to denote the ground truth of an outcome, let $\hat{Y}$ to denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold. For non-binary prediction, such as a score, we use $\hat{V}$.

@@

% \begin{definition}[Independence\cite{barocas2023fairness}]\label{def:independence}
% $(S, \hat{Y})$ satisfy independence if and only if $S \bot \hat{Y}$; that is
% \[
% P[\hat{Y} = 1 | S = 1] = P[\hat{Y} = 1 | S \neq 1]
% \]
% A relaxation of independence on a threshold is
% \[
% \abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon
% \]
% \end{definition}

% \begin{definition}[Separation\cite{barocas2023fairness}]\label{def:separation}
% $(S, Y, \hat{Y})$ satisfy separation if and only if $S \bot \hat{Y} | Y$; that is
% \begin{align*}
% P[\hat{Y} = 1 | S = 1, Y = 1] & = P[\hat{Y} = 1 | S \neq 1, Y = 1] \\
% P[\hat{Y} = 1 | S = 1, Y = 0] & = P[\hat{Y} = 1 | S \neq 1, Y = 0]
% \end{align*}
% A relaxation of independence on a threshold is
% \begin{align*}
% \abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} & \leq \epsilon \\
% \abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} & \leq \epsilon
% \end{align*}
% \end{definition}

% \begin{definition}[Sufficiency\cite{barocas2023fairness}]\label{def:separation}
% $(S, Y, \hat{Y})$ satisfy sufficiency if and only if $S \bot Y | \hat{Y}$; that is
% \begin{align*}
% P[Y = 1 | S = 1, \hat{Y} = 1] & = P[Y = 1 | S \neq 1, \hat{Y} = 1] \\
% P[Y = 1 | S = 1, \hat{Y} = 0] & = P[Y = 1 | S \neq 1, \hat{Y} = 0]
% \end{align*}
% A relaxation of independence on a threshold is
% \begin{align*}
% \abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} & \leq \epsilon \\
% \abs{P[Y = 1 | S = 1, \hat{Y} = 0] - P[Y = 1 | S \neq 1, \hat{Y} = 0]} & \leq \epsilon
% \end{align*}
% \end{definition}

% The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.

% The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling from the fitted Markov random field.

>>>>

Let $\set{X_i}$ be a set of discrete random variables indexed by a graph $G = (V,E)$, where $V$ represents the random variables $X_i$s and $E$ represents dependencies between these random variables. A \emph{Markov random field} is a probability distribution over $X_i$s, such that each random variable $X_i$, given its neighborhood in $G$, is conditionally independent of all other variables. Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent. As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{murphy2023probabilistic}.

@@

For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ denote the ground truth of an outcome, let $\hat{Y}$ denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold. For non-binary prediction, such as a score, we use $\hat{V}$.

@@

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to inference from the fitted Markov random field.
